### 2019-04-29 tii/tex/intro.tex
Submit version 1.0

\section{Introduction}\label{sec:introduction}
\IEEEPARstart{W}{e} are in an era of data explosion --- 2.5 quintillion bytes of data are created every day according to IBM's report\footnote{http://www-01.ibm.com/software/data/bigdata/}.
{\color{blue}
In \textit{industry 4.0}, an increasing number of IoT sensors are embedded in the industrial production line \cite{lade2017manufacturing}.
During the manufacturing process, the information about the assembly lines, stations, and machines is continuously generated and collected.
Using distributed computing frameworks to analyze industrial big-data is an inevitable trend \cite{lee2014service}.
% \cite{ibmreport}.
% These data come from a variety of industry, e.g., records in industrial production, digital pictures and videos in social networks, and sensors used for Internet of Things (IoT).
% These data come from a variety of industries, e.g., e-commerce, telecommunications, media, retail customers and social networks.
% \cite{chen2012interactive}.
% Whether the data is generated from industrial production or social networks, the analysis methods are almost MapReduce-related\cite{lv2017next}.
% Nowadays, the real challenge of big data is not how to collect it, but how to manage it logically and efficiently\cite{lv2017next}.
Several sophisticated frameworks are used in industrial big-data analysis such as Hadoop MapReduce\footnote{http://hadoop.apache.com/}, Spark \cite{spark}, and Storm\footnote{http://storm.apache.com/}.
% The analysis method for these industrial big data mainly relies on MapReduce-liked frameworks, such as Hadoop MapReduce\footnote{http://hadoop.apache.com/}, Spark\cite{spark}, and Storm\footnote{http://storm.apache.com/}.
% Recent years have witnessed the widespread use of sophisticated frameworks, such as Hadoop MapReduce\footnote{http://hadoop.apache.com/}, Dryad \cite{dryad}, Spark \cite{spark}, and Apache Tez \cite{tez}.
Industrial big-data is more structured, correlated, and ready for analytics than traditional big-data, because industrial big-data is generated by automated equipment \cite{basanta2018efficient, lv2017next}.
}

{\color{blue}
According to a cross-industry study \cite{chen2012interactive}, both industrial and traditional big-data share a characteristic during analytical processing --- a small fraction of the daily workload uses well over 90\% of the cluster’s resources, and these workloads often contain a huge shuffle size. 
According to another MapReduce trace analysis from Facebook, the shuffle phase accounts for $33\%$ of the job completion time on average, and up to $70\%$ in shuffle-heavy jobs \cite{managing}.
The shuffle phase is crucial and heavily affecting the end-to-end application performance.
Most of the popular frameworks define jobs as directed acyclic graphs (DAGs), such as map-reduce pipeline in Hadoop MapReduce, lineage of resilient distributed datasets (RDDs) in Spark, vertices and edges in Dryad \cite{dryad} and Tez \cite{tez}, etc.
Despite the differences among data-intensive frameworks, the shuffle phase is always essential as communication between successive computation stages.
}

\begin{figure}
	\centering
	\includegraphics
		[width=1\linewidth]
		{fig/workflow}
	\caption{Workflow Comparison between Legacy DAG Computing Frameworks and Frameworks with SCache}
	\label{fig:workflow}
\end{figure}
{\color{blue}
Although continuous efforts of performance optimization have been made among a variety of computing frameworks\cite{chen2017parallel, duan2016selection, tang2018intermediate, sync, tachyon, heintz2016end, zhang2015prism, cheng2017improving, chen2017heterogeneous, wasi2017comprehensive, chen2013tiled}, the shuffle phase is often poorly optimized in practice.
In particular, we observe that one major deficiency lies in the coupled scheduling among different system resources.
}
%In the current practice, the shuffle phase is often split into two parts --- \textit{shuffle read} and \textit{shuffle write}. 
As Figure \ref{fig:workflow} shows, the \textit{shuffle write} is responsible for writing intermediate results to disk, which is attached to the tasks in ancestor stages (i.e., map task).  
And the \textit{shuffle read} fetches intermediate results from remote disks through network, which is commonly integrated as part of the tasks in descendant stages (i.e., reduce task). 
Once scheduled, a fixed bundle of resources (i.e., CPU, memory, disk, and network) named \textit{slot} is assigned to a task, and the resources are released only after the task finishes.
{\color{blue}
Such task aggregation together with the coupled scheduling effectively simplifies task management.
}
However, since a cluster has a limited number of slots, attaching the I/O intensive shuffle phase to the CPU/memory intensive computation phase results in a poor multiplexing between computational and I/O resources.
%The map task in Figure \ref{fig:workflow} well explains such deficiency: the I/O resource allocated to the stage is always idle during the computation time, and the computation/memory resource is totally wasted during the shuffle write attached to it, and vice versa.

Moreover, the shuffle read phase introduces all-to-all communication pattern across the network, and such network I/O procedure is also poorly coordinated.
Note that the shuffle read phase starts fetching data only after the corresponding reduce task starts.
Meanwhile, the reduce tasks belonging to the same execution phase are scheduled at the same time by default. 
As a result, all the corresponding reduce tasks start fetching shuffle data almost simultaneously.
Such synchronized network communication causes a burst demand for network I/O, which in turn greatly enlarges the shuffle read completion time. 
To desynchronize the network communication, an intuitive way is to launch some tasks in the descendent stage earlier, such as "slow-start" from Hadoop MapReduce.
% However, such early-start is by no means a panacea. 
% This is because the early-start always introduces an extra early allocation of the slot leading to a slow execution of the current stage.
{\color{blue}
However, such early-start has several deficiencies.
First, the early-start always introduces an extra early allocation of the slot leading to a slow execution of the current stage.
Second, the early-start can not fully overlap the shuffle phases and the descendent stage. Due to the shuffle phases are coupled with the reduce phases and the size of slots is limited, only parts of reduce tasks can be early-start. 
Last but not least, it is hard to find the optimal time to begin the early-start. If too early, the descendent stages are not ready to output enough intermediate data for the shuffle. If too late, the idle network resource is wasted.
}

@@

% {\color{red}
% We have implemented SCache and a customized Apache Spark \cite{apachespark}. The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster. We conduct basic test GroupByTest. We also evaluate Terasort \cite{spark-tera} benchmark and standard workloads like TPC-DS \cite{tpcds} for multi-tenant modeling. In a nutshell, SCache can eliminate explicit shuffle process by at most $89\%$ in varied application scenarios. More impressively, SCache reduces $~40\%$ of overall completion time of TPC-DS queries on average.
% }
{\color{blue}
We also propose a new performance model called \textit{Framework Resources Quantification} (FRQ) model. The FRQ model quantifies computing and I/O resources and visualizes the resources scheduling strategies of DAG frameworks in the time dimension. We use the FRQ model to assist in analyzing the deficiencies of resources scheduling and optimize it. 
% The FRQ model has five parameters: \textit{Input Data Size, Data Conversion Rate, Computation Round Number, Computation Speed,} and \textit{Shuffle  Speed}.
% According to the above five parameters and the scheduling strategy of the DAG framework, the FRQ model is able to predict the execution time of each phase of a computing job. 
% Taking Apache Hadoop MapReduce as a simple DAG computing example, we model each phase of the computing by the FRQ model, including Map, Shuffle, and Reduce.
% By revealing the relationships between the various phases, the FRQ model assists us in discovering the irrationality of resource scheduling during computing (Section \ref{model}).
In the industrial production, the FRQ model can discover the irrationality of resource scheduling in big-data analysis by revealing the relationships between the various phases (Section \ref{model}).
% I/O resources in the map phase are not fully utilized. Furthermore, due to coupling with reduce phase, shuffle phase delays the execution time of reduce phase. 
% This situation will be amplified in shuffle-heavy tasks.
}

{\color{blue}
We have implemented SCache on both Apache Spark \cite{apachespark} and Hadoop MapReduce. 
% We have also designed a performance model called FRQ model to analyze the shuffle optimization of SCache and predict the execution time of each phase of a computing job. 
The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster on both Apache Spark and Apache Hadoop. On Apache Spark, we conduct a basic test - \textit{GroupByTest}. We also evaluate the system with Terasort\footnote{https://github.com/ehiggs/spark-terasort} benchmark and standard workloads like TPC-DS\footnote{http://www.tpc.org/tpcds/} for multi-tenant modeling. On Apache Hadoop, we focus on Terasort benchmark. In a nutshell, SCache can eliminate explicit shuffle time by at most $89\%$ in varied applications. More impressively, SCache reduces $~40\%$ of overall completion time of TPC-DS queries on average on Apache Spark. On Apache Hadoop, SCache optimizes end-to-end Terasort completion time by $15\%$.
}

>>>>

\section{Introduction}\label{sec:introduction}
\IEEEPARstart{W}{e} are in an era of data explosion --- 2.5 quintillion bytes of data are created every day according to IBM's report\footnote{http://www-01.ibm.com/software/data/bigdata/}.
{\color{black}
In \textit{industry 4.0}, an increasing number of IoT sensors are embedded in the industrial production line \cite{lade2017manufacturing}.
During the manufacturing process, the information about the assembly lines, stations, and machines is continuously generated and collected.
Using distributed computing frameworks to analyze industrial big-data is an inevitable trend \cite{lee2014service}.
% \cite{ibmreport}.
% These data come from a variety of industry, e.g., records in industrial production, digital pictures and videos in social networks, and sensors used for Internet of Things (IoT).
% These data come from a variety of industries, e.g., e-commerce, telecommunications, media, retail customers and social networks.
% \cite{chen2012interactive}.
% Whether the data is generated from industrial production or social networks, the analysis methods are almost MapReduce-related\cite{lv2017next}.
% Nowadays, the real challenge of big data is not how to collect it, but how to manage it logically and efficiently\cite{lv2017next}.
Several sophisticated frameworks are used in industrial big-data analysis such as Hadoop MapReduce\footnote{http://hadoop.apache.com/}, Spark \cite{spark}, and Storm\footnote{http://storm.apache.com/}.
% The analysis method for these industrial big data mainly relies on MapReduce-liked frameworks, such as Hadoop MapReduce\footnote{http://hadoop.apache.com/}, Spark\cite{spark}, and Storm\footnote{http://storm.apache.com/}.
% Recent years have witnessed the widespread use of sophisticated frameworks, such as Hadoop MapReduce\footnote{http://hadoop.apache.com/}, Dryad \cite{dryad}, Spark \cite{spark}, and Apache Tez \cite{tez}.
Industrial big-data is more structured, correlated, and ready for analytics than traditional big-data, because industrial big-data is generated by automated equipment \cite{basanta2018efficient, lv2017next}.
}

{\color{black}
According to a cross-industry study \cite{chen2012interactive}, both industrial and traditional big-data share a characteristic during analytical processing --- a small fraction of the daily workload uses well over 90\% of the cluster’s resources, and these workloads often contain a huge shuffle size. 
According to another MapReduce trace analysis from Facebook, the shuffle phase accounts for $33\%$ of the job completion time on average, and up to $70\%$ in shuffle-heavy jobs \cite{managing}.
The shuffle phase is crucial and heavily affecting the end-to-end application performance.
Most of the popular frameworks define jobs as directed acyclic graphs (DAGs), such as map-reduce pipeline in Hadoop MapReduce, lineage of resilient distributed datasets (RDDs) in Spark, vertices and edges in Dryad \cite{dryad} and Tez \cite{tez}, etc.
Despite the differences among data-intensive frameworks, the shuffle phase is always essential as communication between successive computation stages.
}

\begin{figure}
	\centering
	\includegraphics
		[width=1\linewidth]
		{fig/workflow}
	\caption{Workflow Comparison between Legacy DAG Computing Frameworks and Frameworks with SCache}
	\label{fig:workflow}
\end{figure}
{\color{black}
Although continuous efforts of performance optimization have been made among a variety of computing frameworks\cite{chen2017parallel, duan2016selection, tang2018intermediate, sync, tachyon, heintz2016end, zhang2015prism, cheng2017improving, chen2017heterogeneous, wasi2017comprehensive, chen2013tiled}, the shuffle phase is often poorly optimized in practice.
In particular, we observe that one major deficiency lies in the coupled scheduling among different system resources.
}
%In the current practice, the shuffle phase is often split into two parts --- \textit{shuffle read} and \textit{shuffle write}. 
As Figure \ref{fig:workflow} shows, the \textit{shuffle write} is responsible for writing intermediate results to disk, which is attached to the tasks in ancestor stages (i.e., map task).  
And the \textit{shuffle read} fetches intermediate results from remote disks through network, which is commonly integrated as part of the tasks in descendant stages (i.e., reduce task). 
Once scheduled, a fixed bundle of resources (i.e., CPU, memory, disk, and network) named \textit{slot} is assigned to a task, and the resources are released only after the task finishes.
{\color{black}
Such task aggregation together with the coupled scheduling effectively simplifies task management.
}
However, since a cluster has a limited number of slots, attaching the I/O intensive shuffle phase to the CPU/memory intensive computation phase results in a poor multiplexing between computational and I/O resources.
%The map task in Figure \ref{fig:workflow} well explains such deficiency: the I/O resource allocated to the stage is always idle during the computation time, and the computation/memory resource is totally wasted during the shuffle write attached to it, and vice versa.

Moreover, the shuffle read phase introduces all-to-all communication pattern across the network, and such network I/O procedure is also poorly coordinated.
Note that the shuffle read phase starts fetching data only after the corresponding reduce task starts.
Meanwhile, the reduce tasks belonging to the same execution phase are scheduled at the same time by default. 
As a result, all the corresponding reduce tasks start fetching shuffle data almost simultaneously.
Such synchronized network communication causes a burst demand for network I/O, which in turn greatly enlarges the shuffle read completion time. 
To desynchronize the network communication, an intuitive way is to launch some tasks in the descendent stage earlier, such as "slow-start" from Hadoop MapReduce.
% However, such early-start is by no means a panacea. 
% This is because the early-start always introduces an extra early allocation of the slot leading to a slow execution of the current stage.
{\color{black}
However, such early-start has several deficiencies.
First, the early-start always introduces an extra early allocation of the slot leading to a slow execution of the current stage.
Second, the early-start can not fully overlap the shuffle phases and the descendent stage. Due to the shuffle phases are coupled with the reduce phases and the size of slots is limited, only parts of reduce tasks can be early-start. 
Last but not least, it is hard to find the optimal time to begin the early-start. If too early, the descendent stages are not ready to output enough intermediate data for the shuffle. If too late, the idle network resource is wasted.
}

@@

% {\color{red}
% We have implemented SCache and a customized Apache Spark \cite{apachespark}. The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster. We conduct basic test GroupByTest. We also evaluate Terasort \cite{spark-tera} benchmark and standard workloads like TPC-DS \cite{tpcds} for multi-tenant modeling. In a nutshell, SCache can eliminate explicit shuffle process by at most $89\%$ in varied application scenarios. More impressively, SCache reduces $~40\%$ of overall completion time of TPC-DS queries on average.
% }
{\color{black}
We also propose a new performance model called \textit{Framework Resources Quantification} (FRQ) model. The FRQ model quantifies computing and I/O resources and visualizes the resources scheduling strategies of DAG frameworks in the time dimension. We use the FRQ model to assist in analyzing the deficiencies of resources scheduling and optimize it. 
% The FRQ model has five parameters: \textit{Input Data Size, Data Conversion Rate, Computation Round Number, Computation Speed,} and \textit{Shuffle  Speed}.
% According to the above five parameters and the scheduling strategy of the DAG framework, the FRQ model is able to predict the execution time of each phase of a computing job. 
% Taking Apache Hadoop MapReduce as a simple DAG computing example, we model each phase of the computing by the FRQ model, including Map, Shuffle, and Reduce.
% By revealing the relationships between the various phases, the FRQ model assists us in discovering the irrationality of resource scheduling during computing (Section \ref{model}).
In the industrial production, the FRQ model can discover the irrationality of resource scheduling in big-data analysis by revealing the relationships between the various phases (Section \ref{model}).
% I/O resources in the map phase are not fully utilized. Furthermore, due to coupling with reduce phase, shuffle phase delays the execution time of reduce phase. 
% This situation will be amplified in shuffle-heavy tasks.
}

{\color{black}
We have implemented SCache on both Apache Spark \cite{apachespark} and Hadoop MapReduce. 
% We have also designed a performance model called FRQ model to analyze the shuffle optimization of SCache and predict the execution time of each phase of a computing job. 
The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster on both Apache Spark and Apache Hadoop. On Apache Spark, we conduct a basic test - \textit{GroupByTest}. We also evaluate the system with Terasort\footnote{https://github.com/ehiggs/spark-terasort} benchmark and standard workloads like TPC-DS\footnote{http://www.tpc.org/tpcds/} for multi-tenant modeling. On Apache Hadoop, we focus on Terasort benchmark. In a nutshell, SCache can eliminate explicit shuffle time by at most $89\%$ in varied applications. More impressively, SCache reduces $~40\%$ of overall completion time of TPC-DS queries on average on Apache Spark. On Apache Hadoop, SCache optimizes end-to-end Terasort completion time by $15\%$.
}

### 2019-04-29 tii/tex/model.tex
Submit version 1.0

{\color{blue}
\section{Framework Resources Quantification Model}\label{model}

In this section, we introduce \textit{Framework Resources Quantification} (FRQ) model to describe the performance of DAG frameworks.
The FRQ model quantifies computing and I/O resources and visualizes them in the time dimension. According to the FRQ model, we can calculate the execution time required by the application under any circumstances, including different DAG frameworks, hardware environments, and so on. Therefore, the FRQ model is able to help us analyze the resources scheduling of DAG framework and evaluate their performance. We will first introduce the FRQ model in Subsection \ref{model_overview}. In the following Subsection \ref{model_analysis}, we will use the FRQ model to describe three different computation jobs and analyze their performance. In the last Subsection \ref{model_evaluation}, we will use the actual experimental results to evaluate the FRQ model.

@@

\begin{figure*}
    \centering
	\includegraphics[width=0.85\textwidth]{fig/model_basic}
	\caption{\color{blue}Framework Resources Quantification (FRQ) Model with Full Parallel MapReduce}
    \label{fig:model_basic}
    \vspace{-1em}
\end{figure*}
The FRQ model calculates the execution time of each phase of the job with these five parameters. As shown in Figure \ref{fig:model_basic}, the total execution time of a job is the sum of the map phase time and reduce phase time:
\begin{equation}
\label{equation_Tjob}
\begin{aligned}
    T_{Job} &= T_{Map} + T_{Reduce}
\end{aligned}
\end{equation}

@@

\begin{figure*}
	\centering
	\begin{subfigure}{0.47\linewidth}
		\includegraphics[width=\linewidth]{fig/model_original}
		\caption{\color{blue}Full Serial MapReduce}
		\label{fig:model_original}
	\end{subfigure}
	\begin{subfigure}{0.47\linewidth}
		\includegraphics[width=\linewidth]{fig/model_hadoop}
		\caption{\color{blue}Half Parallel MapReduce}
		\label{fig:model_hadoop}
	\end{subfigure}
	\caption{\color{blue}Framework Resources Quantification (FRQ) Model with Different Scheduling Strategies}
	\label{fig:model_strategies}
\end{figure*}

@@

\begin{figure*}
	\centering
	\begin{subfigure}{0.47\linewidth}
		\includegraphics[width=\linewidth]{fig/model_scache1}
		\caption{\color{blue}If \(V_{Map} \times R \ge V_{Shuffle}\)}
		\label{fig:model_scache1}
	\end{subfigure}
	\begin{subfigure}{0.47\linewidth}
		\includegraphics[width=\linewidth]{fig/model_scache2}
		\caption{\color{blue}If \(V_{Map} \times R < V_{Shuffle}\)}
		\label{fig:model_scache2}
	\end{subfigure}
	\caption{\color{blue}Framework Resources Quantification (FRQ) Model with Full Parallel MapReduce in Different Environments}
	\label{fig:model_scache}
\end{figure*}

@@

	\hline
	& 16	& 1	& 2 &	0.65 &	1 &	0.47 &	0.5 &	24.62 &		34.04	 &	21.73 &	26.87 &	51.48	& 55  &		6.39\% \\
	SCache
	& 32	& 1	& 4 &	0.65 &	1 &	0.47 &	0.5 &	49.23 &		68.09	 &	31.16 &	47.58 &	96.81	& 104 & 	6.91\% \\
	& 48	& 1	& 6 &	0.65 &	1 &	0.47 &	0.5 &	73.85 &		102.13 &	40.59 &	68.29 &	142.14	& 151 & 	5.87\% \\
	& 64	& 1	& 8 &	0.65 &	1 &	0.47 &	0.5 &	98.46 &		136.17 &	50.02 &	89.01 &	187.47	& 193 & 	2.87\% \\
	\hline
	& 16	& 1 & 2 &	0.65 &	1 &	0.47 &	0.6 &	24.62 &		34.04	&	34.04	&	36.43	&	61.04	&	73	&	16.38\%	\\
	Legacy
	& 32	& 1 & 4 &	0.65 &	1 &	0.47 &	0.6 &	49.23 &		68.09	&	68.09	&	72.85	&	122.08	&	135	&	9.57\%	\\
	& 48	& 1 & 6 &	0.65 &	1 &	0.47 &	0.6 &	73.85 &		102.13	&	102.13	&	109.28	&	183.12	&	188	&	2.59\%	\\
	& 64	& 1 & 8 &	0.65 &	1 &	0.47 &	0.6 &	98.46 &		136.17	&	136.17	&	145.70	&	244.16	&	249	&	1.94\%	\\
	\hline
	\end{tabular}
}
\(D\): GB, \(V_{i}\): GB/s, \(T_{i}\): s
\caption{\color{blue}Hadoop MapReduce on 4 nodes cluster in the FRQ model}
\label{table1}
\end{table*}
% \subsection{Performance Analysis}\label{model_performance_analysis}

@@

	\hline
	\end{tabular}
}
\(D\): GB, \(V_{i}\): GB/s, \(T_{i}\): s
\caption{\color{blue}Hadoop MapReduce on 50 AWS m4.xlarge nodes cluster in the FRQ model}
\label{table2}
\end{table*}

@@

\begin{figure*}
	\centering
	\begin{subfigure}{.42\linewidth}
		\includegraphics[width=\linewidth]{fig/hadoop_net1}
		\caption{\color{blue}If \(V_{Map} \times R \ge V_{Shuffle}\)}
		\label{fig:hadoop_net1}
	\end{subfigure}
	\begin{subfigure}{.42\linewidth}
		\includegraphics[width=\linewidth]{fig/hadoop_net2}
		\caption{\color{blue}If \(V_{Map} \times R < V_{Shuffle}\)}
		\label{fig:hadoop_net2}
	\end{subfigure}
	\caption{\color{blue}Network utilization on Hadoop MapReduce with SCache}
	\label{fig:hadoop_net}
\end{figure*}

>>>>

{\color{black}
\section{Framework Resources Quantification Model}\label{model}

In this section, we introduce \textit{Framework Resources Quantification} (FRQ) model to describe the performance of DAG frameworks.
The FRQ model quantifies computing and I/O resources and visualizes them in the time dimension. In the industrial production, the FRQ model is able to predict the execution time required by the application under any circumstances, including different DAG frameworks, hardware environments, etc. The FRQ model assist us in analyzing the resource scheduling of DAG framework and evaluate their performance. We will first introduce the FRQ model in Subsection \ref{model_overview}. In the following Subsection \ref{model_analysis}, we will use the FRQ model to describe three different computation jobs and analyze their performance. In the last Subsection \ref{model_evaluation}, we will use the actual experimental results to evaluate the FRQ model.

@@

\begin{figure*}
    \centering
	\includegraphics[width=0.85\textwidth]{fig/model_basic}
	\caption{\color{black}Framework Resources Quantification (FRQ) Model with Full Parallel MapReduce}
    \label{fig:model_basic}
    \vspace{-1em}
\end{figure*}
The FRQ model calculates the execution time of each phase of the job with these five parameters. As shown in Figure \ref{fig:model_basic}, the total execution time of a job is the sum of the map phase time and reduce phase time:
\begin{equation}
\label{equation_Tjob}
\begin{aligned}
    T_{Job} &= T_{Map} + T_{Reduce}
\end{aligned}
\end{equation}

@@

\begin{figure*}
	\centering
	\begin{subfigure}{0.47\linewidth}
		\includegraphics[width=\linewidth]{fig/model_original}
		\caption{\color{black}Full Serial MapReduce}
		\label{fig:model_original}
	\end{subfigure}
	\begin{subfigure}{0.47\linewidth}
		\includegraphics[width=\linewidth]{fig/model_hadoop}
		\caption{\color{black}Half Parallel MapReduce}
		\label{fig:model_hadoop}
	\end{subfigure}
	\caption{\color{black}Framework Resources Quantification (FRQ) Model with Different Scheduling Strategies}
	\label{fig:model_strategies}
\end{figure*}

@@

\begin{figure*}
	\centering
	\begin{subfigure}{0.47\linewidth}
		\includegraphics[width=\linewidth]{fig/model_scache1}
		\caption{\color{black}If \(V_{Map} \times R \ge V_{Shuffle}\)}
		\label{fig:model_scache1}
	\end{subfigure}
	\begin{subfigure}{0.47\linewidth}
		\includegraphics[width=\linewidth]{fig/model_scache2}
		\caption{\color{black}If \(V_{Map} \times R < V_{Shuffle}\)}
		\label{fig:model_scache2}
	\end{subfigure}
	\caption{\color{black}Framework Resources Quantification (FRQ) Model with Full Parallel MapReduce in Different Environments}
	\label{fig:model_scache}
\end{figure*}

@@

	\hline
	& 16	& 1	& 2 &	0.65 &	1 &	0.47 &	0.5 &	24.62 &		34.04	 &	21.73 &	26.87 &	51.48	& 55  &		6.39\% \\
	SCache
	& 32	& 1	& 4 &	0.65 &	1 &	0.47 &	0.5 &	49.23 &		68.09	 &	31.16 &	47.58 &	96.81	& 104 & 	6.91\% \\
	& 48	& 1	& 6 &	0.65 &	1 &	0.47 &	0.5 &	73.85 &		102.13 &	40.59 &	68.29 &	142.14	& 151 & 	5.87\% \\
	& 64	& 1	& 8 &	0.65 &	1 &	0.47 &	0.5 &	98.46 &		136.17 &	50.02 &	89.01 &	187.47	& 193 & 	2.87\% \\
	\hline
	& 16	& 1 & 2 &	0.65 &	1 &	0.47 &	0.6 &	24.62 &		34.04	&	34.04	&	36.43	&	61.04	&	73	&	16.38\%	\\
	Legacy
	& 32	& 1 & 4 &	0.65 &	1 &	0.47 &	0.6 &	49.23 &		68.09	&	68.09	&	72.85	&	122.08	&	135	&	9.57\%	\\
	& 48	& 1 & 6 &	0.65 &	1 &	0.47 &	0.6 &	73.85 &		102.13	&	102.13	&	109.28	&	183.12	&	188	&	2.59\%	\\
	& 64	& 1 & 8 &	0.65 &	1 &	0.47 &	0.6 &	98.46 &		136.17	&	136.17	&	145.70	&	244.16	&	249	&	1.94\%	\\
	\hline
	\end{tabular}
}
\(D\): GB, \(V_{i}\): GB/s, \(T_{i}\): s
\caption{\color{black}Hadoop MapReduce on 4 nodes cluster in the FRQ model}
\label{table1}
\end{table*}
% \subsection{Performance Analysis}\label{model_performance_analysis}

@@

	\hline
	\end{tabular}
}
\(D\): GB, \(V_{i}\): GB/s, \(T_{i}\): s
\caption{\color{black}Hadoop MapReduce on 50 AWS m4.xlarge nodes cluster in the FRQ model}
\label{table2}
\end{table*}

@@

\begin{figure*}
	\centering
	\begin{subfigure}{.42\linewidth}
		\includegraphics[width=\linewidth]{fig/hadoop_net1}
		\caption{\color{black}If \(V_{Map} \times R \ge V_{Shuffle}\)}
		\label{fig:hadoop_net1}
	\end{subfigure}
	\begin{subfigure}{.42\linewidth}
		\includegraphics[width=\linewidth]{fig/hadoop_net2}
		\caption{\color{black}If \(V_{Map} \times R < V_{Shuffle}\)}
		\label{fig:hadoop_net2}
	\end{subfigure}
	\caption{\color{black}Network utilization on Hadoop MapReduce with SCache}
	\label{fig:hadoop_net}
\end{figure*}
